### 2016-09-30 features.tex
Add sympy.calculus to the list of calculus submodules

\begin{longtable}[htbc]{>{\raggedright}p{0.30\linewidth}p{0.63\linewidth}}
\caption{SymPy Features and Descriptions\label{features-table}}\\
\toprule
\textbf{Feature (submodules)} & \textbf{Description} \\
\midrule
Calculus (\texttt{sympy.core}, \texttt{sympy.series}, \texttt{sympy.integrals}) & Algorithms for computing derivatives, integrals, and limits.\\

>>>>

\begin{longtable}[htbc]{>{\raggedright}p{0.30\linewidth}p{0.63\linewidth}}
\caption{SymPy Features and Descriptions\label{features-table}}\\
\toprule
\textbf{Feature (submodules)} & \textbf{Description} \\
\midrule
Calculus (\texttt{sympy.core}, \texttt{sympy.calculus}, \texttt{sympy.integrals}, \texttt{sympy.series}) & Algorithms for computing derivatives, integrals, and limits.\\
